---
title: "Reverse geocoding"
author: "GML"
format: html
editor: visual
---

## Reverse Geo coding

We use geographical coordinates to obtain information on the distributions of KBAs according to administrative organization (localities, provinces, departments).

```{r}


#install.packages('tidygeocoder')
#install.packages("tidyverse")
library(dplyr, warn.conflicts = FALSE)
library(tidygeocoder)
library(tidyverse)

```

Reading a file from (KBA webpage)\[https://www.keybiodiversityareas.org/sites-table\]

```{r}

data_KBAs_Peru <- read.csv("../data/Sites table - keybiodiversityareas.org.csv",
                           header=TRUE, 
                           sep = ",")

head(data_KBAs_Peru)
poi <- data_KBAs_Peru[,c(9,10)]
```

We want to get geographical details of provinces/regions to quantify the numbers of KBAs in Cajamarca and Amazonas, which are the areas of interest and where the collections of KUELAP mainly come from.

```{r}

# Where are the KBAs
locs_KBAs <- tidygeocoder::reverse_geo(long = poi[, "Longitude"], 
                          lat = poi[, "Latitude"], 
                          method = "osm")

# How many in Amazonas

locs_KBAs[grepl("Amazonas", locs_KBAs$address),]#14
locs_KBAs[grepl("Cajamarca", locs_KBAs$address),]#22


```

These were 234 coordinates (KBAs) and the result was relatively quick, the question is whether this works with large amounts of data.
